---
title: "Report for LAB5"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Report for LAB5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab5)
```

my_API Fuction: Access the Data in the API.
Kolada database: The open and free database for municipalities and regions.
This data set contains the code of regions and the name of the schools in each region  criteria.
The function is used to measure the number of schools in each region that is the part of each municipality KPI.
Input: URL/ output: datafram of the codes of region and the number of schools in each region
rawToChar & fromJSON is used to change the structure of data to some readble R Data

## Library:
**httr**

**jsonlite**


## Function: 
The function is used to measure the number of schools in each region that is the part of each municipality KPI.
Input: URL/ output: datafram of the codes of region and the number of schools in each region
rawToChar & fromJSON is used to change the structure of data to some readble R Data
```{R function code}
my_API <- function(url){
  res <- httr::GET(url)
  #stopifnot()
  my_data <-  jsonlite::fromJSON(rawToChar(res$content))
  #print(my_data)
  municipality_name <- c(unique(my_data$values$municipality))
  number_schools <- c()
  for (value in municipality_name){
    count=nrow(subset(my_data$values,my_data$values$municipality==value))
    number_schools <- c(count,number_schools)
  }
  df <- data.frame(municipality_name,number_schools)
  return(df)
}

```
 
## How to use Function:

Function my_API gets a URL as an input and the output would be a data frame of 2 variables **municipality_name** and **number_schools**
municipality_name is a list of region codes as an character
number_schools is a list of number of schools in each region as an integer.

### Example 
```{R input example, echo=TRUE}
output <- my_API("http://api.kolada.se/v2/ou?title=skola")
head(output)
```
 
### Note:
The output of my_API function is used as an input for shiny app which gets the region codes and shows the number of schools in an iterative widget. Moreover shiny app has a table of all variable and user can filter based on any input.
 
